### 2016-02-01 Projects/DelCo_2012/Report/DelCo_2012.tex
add } to fix figure error in report
edits to CAFS report

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/West_Structure/DelCo_2012_West_Structure_Plain}
	\caption{Delaware County, PA Burn Building Layout}
	\label{fig:Delaware_County,_PA_Burn_Building_Layout}
\end{figure}

@@

\subsection{Concrete Block Structures}
\label{sec:Experimental Structures}

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Plain}
	\caption{Floor Plan of the Test Structure.}
	\label{fig:Test_Structure_Floor_Plan}
\end{figure}

@@

The west structure was modified to add second story to be able to test larger fires and remote effects from suppression. The outer walls of the bottom floor of the two-story structure were identical to that of the single story structures described above but with an open floor plan. The interior dimensions were 6.1~m (20~ft) wide, 11~m (36~ft) long and 2.4~m (8~ft) high. The second story walls were framed with steel studs and track. The studs were set to 0.40~m (16~in) centers.

@@

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Instrumentation}
	\caption{Instrumentation Schematic for the Fire Suppression Experiments.}
	\label{fig:Fire_Suppression_Instrumentation_Dimensions}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Pallets}
	\caption{Wood Fuel Load Dimensions.}
	\label{fig:Wood_Fuel_Load_Dimensions}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Pictures/Furniture_Fuel_Load}
	\caption{Furniture Fuel Load.}
	\label{fig:Furniture_Fuel_Load}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Furniture}
	\caption{Furniture Fuel Load Dimensions.}
	\label{fig:Furniture_Fuel_Load_Dimensions}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/West_Structure/DelCo_2012_West_Structure_Pallets}
	\caption{Furniture Fuel Load in First Floor of Two-Story Structure.}
	\label{fig:furniture_2story}
\end{figure

@@

>>>>

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/West_Structure/DelCo_2012_West_Structure_Plain}
	\caption{Dimensioned Floor Plan Burn Building Layout}
	\label{fig:Delaware_County,_PA_Burn_Building_Layout}
\end{figure}

@@

\subsection{Concrete Block Structures}
\label{sec:Experimental Structures}
\subsubsection*{Single Story Structures}

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Plain}
	\caption{Dimensioned Floor Plan of the Test Structure.}
	\label{fig:Test_Structure_Floor_Plan}
\end{figure}

@@

\subsubsection*{2-Story Structure}

The west structure was modified to add second story to test larger fires and remote suppression effects (cf. Fig~\ref{fig:delco_2story}).

@@

The outer walls of the bottom floor of the two-story structure were identical to that of the single story structures described above but with an open floor plan. The interior dimensions were 6.1~m (20~ft) wide, 11~m (36~ft) long and 2.4~m (8~ft) high. Figure~\ref{fig:dimensioned_first_2story} shows the dimensions of the reconfigured first floor. A stairwell was built to connect the floors. Stairs started 1.6~m (5.25~ft) off the South wall with a width of 1.2~m (4~ft) off the East wall. The second story walls were wood framed with 51~mm (2~in) by 102~mm (4~in) studs. The studs were set to 0.40~m (16~in) centers. The interior  walls were protected by 16~mm (5/8~in) fire rated gypsum board, 16~mm (5/8~in) durarock board, and a second layer of 16~mm (5/8~in) fire rated gypsum board. The exterior walls were protected with 11~mm (7/16~in) oriented strand board and 8~mm (5/16~in) fiber cement lap siding. Figure~\ref{fig:dimensioned_second_2story} shows the dimensions of the second story of the modified west structure.

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_1st_Floor_Plain}
	\caption{Dimensioned Floor Plan of First Floor of Two Story Structure.}
	\label{fig:dimensioned_first_2story}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_2nd_Floor_Plain}
	\caption{Dimensioned Floor Plan of Second Floor of Two Story Structure.}
	\label{fig:dimensioned_second_2story}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Instrumentation}
	\caption{Instrumentation Schematic for the Single Story Fire Suppression Experiments.}
	\label{fig:Fire_Suppression_Instrumentation_Dimensions}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Pallets}
	\caption{Wood Fuel Load in Single Story Structure.}
	\label{fig:Wood_Fuel_Load_Dimensions}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Pictures/Furniture_Fuel_Load}
	\caption{Furniture Fuel Load in Single Story Structure}
	\label{fig:Furniture_Fuel_Load}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Furniture}
	\caption{Furniture Fuel Load Dimensions in Single Story Structure.}
	\label{fig:Furniture_Fuel_Load_Dimensions}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_1st_Floor_Furniture_Only}
	\caption{Furniture Fuel Load in First Floor of Two-Story Structure.}
	\label{fig:furniture_2story}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_1st_Floor_Furniture_Pallets}
	\caption{Furniture and Pallet Fuel Load in First Floor of Two-Story Structure.}
	\label{fig:pallet_furniture_2story}
\end{figure}
